Flatiron cleaning

### 2021-12-03 Rmd/rdi analysis.Rmd
Update rmd

- Select episodedatasource == "Administrations"
```{r drugs episode cleanup}
drugs <- drugs %>% 
  filter(episodedatasource == "Administrations" #& 
           # ismaintenancetherapy == "FALSE" # keep maintenance for a correct recoding of line number
         ) %>%
  # bind with clinical
  inner_join(., clinical_data, 
          by = "patientid") %>% 
  arrange(patientid, episodedate)
```

@@

# rm(drugs, drugs1, therapy_line)
```

@@

  # Calculate expected dose
  mutate(expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
    drugname == "paclitaxel"                  ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(expected_dose = case_when(
    expected_dose > 900 &
      target_auc == 6              ~ 900,
    expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ expected_dose
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
    drugname == "paclitaxel"                  ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    adjusted_expected_dose > 900 &
      target_auc == 6              ~ 900,
    adjusted_expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ adjusted_expected_dose
  )) %>% 
  group_by(patientid) %>%
  mutate(first_treatment_date = case_when(
    str_detect(therapy, "Chemo")                      ~ min(episodedate),
    str_detect(therapy, "Surgery")                    ~ surgerydate,
  )) %>% 
  ungroup() %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  arrange(patientid, episodedate)
```

@@

```

@@

  mutate(RDI_carbo_adj_grp = case_when(
    RDI_carbo_adj >= 0.85              ~ "Adequate dosing",
    RDI_carbo_adj < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_carbo_adj_grp = factor(RDI_carbo_adj_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_carbo_adj_grp1 = case_when(
    RDI_carbo_adj < 0.75               ~ "Highly underdosed",
    RDI_carbo_adj >= 0.75 &
      RDI_carbo_adj < 0.85             ~ "Underdosed",
    RDI_carbo_adj >= 0.85 &
      RDI_carbo_adj < 1.1              ~ "Adequate dosing",
    RDI_carbo_adj >= 1.1               ~ "Overdosing"
  )) %>% 
  mutate(RDI_carbo_adj_grp1 = factor(RDI_carbo_adj_grp1, 
                          levels = c("Adequate dosing",
                                     "Underdosed", 
                                     "Highly underdosed",
                                     "Overdosing"))) %>% 
  mutate(RDI_pacli_adj_grp = case_when(
    RDI_pacli_adj >= 0.85              ~ "Adequate dosing",
    RDI_pacli_adj < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_pacli_adj_grp = factor(RDI_pacli_adj_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_pacli_adj_grp1 = case_when(
    RDI_pacli_adj < 0.75               ~ "Highly underdosed",
    RDI_pacli_adj >= 0.75 &
      RDI_pacli_adj < 0.85             ~ "Underdosed",
    RDI_pacli_adj >= 0.85 &
      RDI_pacli_adj < 1.1              ~ "Adequate dosing",
    RDI_pacli_adj >= 1.1               ~ "Overdosing"
  )) %>% 
  mutate(RDI_pacli_adj_grp1 = factor(RDI_pacli_adj_grp1, 
                          levels = c("Adequate dosing",
                                     "Underdosed", 
                                     "Highly underdosed",
                                     "Overdosing")))
```

@@

Are excluded :  
-	Borderline cases (not invasive ovarian cancer)  
-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)  
```{r}
drugs1 <- Frontline_adjusted %>% 
  mutate(flatiron_rules = case_when(
    days_at_first_drug > 90 | 
      days_at_surg > 90                          ~ "exclude",
    thirty_days_exclusion <= 30                  ~ "exclude",
    exclude == "1"                               ~ "exclude"
  )) %>%
  group_by(patientid) %>% 
  fill(flatiron_rules, .direction = "downup") %>% 
  ungroup()

drugs1 <- drugs1 %>% 
  filter(is.na(flatiron_rules))
```

**At the end of the step 1, we have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.**

@@

- exclude patients whose histology is unknown  
- remove chemotherapy only patients
- include only patients who received platin and/or taxane
- exclude patients who only received neo + surgery
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r}
drugs1 <- drugs1 %>% 
  filter(!is.na(histology)) # loss 287 ################## Will do when bind to drugs

drugs1 <- drugs1 %>%
  filter(!is.na(surgerydate))

drugs1 <- drugs1 %>%
  filter(had_carbo_pacli == "Yes")

drugs1 <- drugs1 %>% 
  filter(treatment_sequence == "neo + surg + adj" |
           treatment_sequence == "surg + adj")

@@

drugs1 <- drugs1 %>%
  # Remove patients with other linename
  filter((linenumber_new == 1 &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin")) |
          (linenumber_new == 2 &
          therapy == "Upfront Chemo" &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Carboplatin"))
         )
```

**At the end of the step 2, we have `r drugs1 %>% distinct(patientid) %>% nrow()` patients.**

@@

```{r}
drugs11 <- drugs1 %>% 
  filter(!(issurgery == "Yes" & is.na(surgerydate)))

drugs11 <- drugs11 %>%
  arrange(patientid, episodedate) %>%
  mutate(ex = case_when(
    interval_surgery_to_adj_start > 3                  ~ "exclude"
  )) %>% 
  filter(is.na(ex))

drugs11 <- drugs11 %>% 
  filter(days_at_first_drug >= 0 &
           (is.na(surgerydate) | days_at_surg >= 0)
         )

drugs11 <- drugs11 %>% 
  # remove these patients who switched C > C 
  filter((!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
            !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj) & 
            therapy == "Upfront Chemo") |
           (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj &
            therapy == "Upfront Surgery")))
```
**At the end of the step 3, we have `r drugs11 %>% distinct(patientid) %>% nrow()` patients.**

@@

- exclude patients with more than 1 line as Neo
- exclude patients with maintenance within their frontline
- exclude patients with more than 6 cycles in Neo, more than 9 cycles **total** in upfront chemo or more than 9 cycles in upfront surgery
```{r}
drugs111 <- drugs11 %>% 
  # Remove patients with more than 1 line as Neo
  filter(is.na(neo_more_more_than_1line))

drugs111 <- drugs111 %>% 
  filter(is.na(whole_frontline_is_maintenance))

drugs111 <- drugs111 %>% 
  filter(is.na(too_many_cycle))
```
**We have `r drugs111 %>% distinct(patientid) %>% nrow()` patients.**

- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxels
```{r}
Frontline <- drugs111 %>% 
  filter(is.na(wrong_pacli_dosedense))

# drugs111 %>% 
#   mutate(n_dose_dense = factor(n_dose_dense)) %>% 
#   select(n_dose_dense, therapy) %>% 
#   tbl_summary(by = therapy)

@@

```{r}
# drugs11 %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(had_neo, had_adj, therapy) %>% 
#   tbl_summary(by = therapy,
#               type = list(had_neo ~ "dichotomous", 
#                           had_adj ~ "dichotomous"),
#               missing = "no")
# # therapy_line %>% 
# #   distinct(patientid, .keep_all = TRUE) %>% 
# #   select(therapy, treatment_sequence) %>% 
# #   tbl_summary(by = therapy)
```

<!-- First table is frontline Neo, second table is frontline Adj. -->
```{r}
# # drugs1 %>% Need to do in Frontline
#   filter(linenumber == 1
#          ) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(linename) %>% 
#   tbl_summary(sort = list(everything() ~ "frequency"))
# 
# # drugs11 %>% 
# #   filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
# #   distinct(patientid, .keep_all = TRUE) %>% 
# #   select(linename) %>% 
# #   tbl_summary(sort = list(everything() ~ "frequency"))
```

@@

<!-- As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI, being underdosed or overdosed -->

<!-- ```{r echo=TRUE} -->
<!-- # Highly underdosed: < 0.75 -->
<!-- # Underdosed: >= 0.75 to <0.85 -->
<!-- # Adequate dosing: >= 0.85 to <1.10 -->
<!-- # Overdosing: >=1.10 -->
<!-- ``` -->
<!-- Fun to see the dots for underdosed patients being located on the right side (higher BMI) and dots for overdosed located on the left (lower BMI) -->
<!-- ```{r, fig.width=12, fig.height=12} -->
<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
<!--   ggplot(aes(x= bmi_at_dx, y = mean_RDI_per_drug, color= RDI_grp1))+ -->
<!--   geom_point(alpha = 0.7, size = 0.75)+ -->
<!--   theme_minimal(base_size = 10)+ -->
<!--   facet_wrap(drugname~ therapy, ncol = 2, scales = "free") -->
<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
<!--   ggplot(aes(x= bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+ -->
<!--   geom_jitter()+ -->
<!--   theme_minimal(base_size = 10)+ -->
<!--   facet_wrap(drugname~ therapy, ncol = 2, scales = "free") -->

<!-- ``` -->
<!-- Here I just wanted to see if we have more or less underdosing / overdosing with BMI -->
<!-- ```{r, fig.width=12, fig.height=12} -->
<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
<!--   ggplot(aes(x= RDI_grp1, fill = drugname))+ -->
<!--   geom_bar(position = position_dodge())+ -->
<!--   theme_minimal(base_size = 10)+ -->
<!--   facet_wrap(. ~ therapy, ncol = 2, scales = "free")+ -->
<!--   coord_flip() -->
<!-- ``` -->

<!-- ```{r, fig.width=12} -->
<!-- # Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
<!-- #   ggplot(aes(x= drugname, fill = RDI_grp1))+ -->
<!-- #   geom_bar(position = position_dodge())+ -->
<!-- #   theme_minimal(base_size = 10)+ -->
<!-- #   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+ -->
<!-- #   coord_flip() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>% -->
<!--   # filter(linenumber_new == "1") %>% -->
<!--   ggplot(aes(x= drugname, fill = RDI_grp1))+ -->
<!--   geom_bar(position = "fill")+ -->
<!--   theme_minimal(base_size = 10)+ -->
<!--   coord_flip()+ -->
<!--   facet_wrap(.~ therapy) -->
<!-- ``` -->
<!-- As you can see above in green, we have a lot of patient who are overdose. -->
<!-- <br> -->
<!-- <br> -->

<!-- ## Hazard Ratio RDI 2 -->

<!-- <span style="color:green">**Table HR**</span>   -->

<!-- ### Univariable -->
<!-- ```{r HR RDI 2} -->
<!-- # Carbo -->
<!-- # tbl1 <- Frontline %>% -->
<!-- #   filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") -->
<!-- # tbl1 <- tbl1 %>% -->
<!-- #   select(vitalstatus, RDI_grp1) %>%  -->
<!-- #   tbl_uvregression(method = survival::coxph, -->
<!-- #                  y = (Surv(time = tbl1$month_at_os_from_treatment, event = tbl1$vitalstatus)), -->
<!-- #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
<!-- tbl2 <- Frontline %>% -->
<!--   filter(drugname == "carboplatin" & therapy == "Upfront Surgery") -->
<!-- tbl2 <- tbl2 %>% -->
<!--   select(vitalstatus, RDI_grp1) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl3 <- Frontline %>% -->
<!--   filter(drugname == "carboplatin" & therapy == "Upfront Chemo") -->
<!-- tbl3 <- tbl3 %>% -->
<!--   select(vitalstatus, RDI_grp1) %>%  -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") -->
<!-- tbl_stack(list(tbl2, tbl3), -->
<!--           group_header = c("carboplatin/Upfront Surgery", "carboplatin/Upfront Chemo")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->

<!-- # Pacli -->
<!-- # tbl7 <- Frontline %>% -->
<!-- #   filter(drugname =="paclitaxel" & chemotherapy_type == "Neoadjuvant") -->
<!-- # tbl7 <- tbl7 %>% -->
<!-- #   select(vitalstatus, RDI_grp1) %>%  -->
<!-- #   tbl_uvregression(method = survival::coxph, -->
<!-- #                  y = (Surv(time = tbl7$month_at_os_from_treatment, event = tbl7$vitalstatus)), -->
<!-- #                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") -->
<!-- tbl8 <- Frontline %>% -->
<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Surgery") -->
<!-- tbl8 <- tbl8 %>% -->
<!--   select(vitalstatus, RDI_grp1) %>% -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl8$month_at_os_from_treatment, event = tbl8$vitalstatus)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**")) -->
<!-- tbl9 <- Frontline %>% -->
<!--   filter(drugname =="paclitaxel" & therapy == "Upfront Chemo") -->
<!-- tbl9 <- tbl9 %>% -->
<!--   select(vitalstatus, RDI_grp1) %>% -->
<!--   tbl_uvregression(method = survival::coxph, -->
<!--                  y = (Surv(time = tbl9$month_at_os_from_treatment, event = tbl9$vitalstatus)), -->
<!--                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level") %>% -->
<!--   modify_header(update = list(label ~ "**paclitaxel/Adjuvant**")) -->
<!-- tbl_stack(list(tbl8, tbl9), -->
<!--           group_header = c("paclitaxel/Upfront Surgery", "paclitaxel/Upfront Chemo")) %>% -->
<!--   bold_labels() %>% -->
<!--   italicize_levels() -->
<!-- ``` -->
<!-- Overdosing can help survival for carboplatin/Adjuvant Upfront Surgery and paclitaxel/Neoadjuvant ?? Loss it when choose correct as reference. -->

>>>>

**We have `r clinical_data %>% distinct(patientid) %>% nrow()` patients info in clinical data.  
**We have `r drugs %>% distinct(patientid) %>% nrow()` patients info in clinical data.

- Select episodedatasource == "Administrations"
```{r drugs episode cleanup}
drugs <- drugs %>% 
  filter(episodedatasource == "Administrations" #& 
           # ismaintenancetherapy == "FALSE" # keep maintenance for a correct recoding of line number
         ) %>%
  # bind with clinical
  inner_join(., clinical_data, 
          by = "patientid") %>% 
  arrange(patientid, episodedate)

drugs %>% distinct(patientid) %>% nrow()
```

@@

# rm(drugs, drugs1, therapy_line)
therapy_cycle %>% distinct(patientid) %>% nrow()
```

@@

  # Calculate expected dose
  mutate(expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (CrCl + 25),
    drugname == "paclitaxel"                  ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(expected_dose = case_when(
    expected_dose > 900 &
      target_auc == 6              ~ 900,
    expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ expected_dose
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    drugname == "carboplatin"                 ~ target_auc * (adjusted_CrCl + 25),
    drugname == "paclitaxel"                  ~ BSA * target_auc 
    # F19EBBFC60652 Can we fill target_auc? No depends of the type of cycle, or maybe by grouping by cycle type and drug
  )) %>% 
  mutate(adjusted_expected_dose = case_when(
    adjusted_expected_dose > 900 &
      target_auc == 6              ~ 900,
    adjusted_expected_dose > 750 &
      target_auc == 5              ~ 750,
    TRUE                           ~ adjusted_expected_dose
  )) %>% 
  group_by(patientid) %>%
  mutate(first_treatment_date = case_when(
    str_detect(therapy, "Chemo")                      ~ min(episodedate),
    str_detect(therapy, "Surgery")                    ~ surgerydate,
  )) %>% 
  ungroup() %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  arrange(patientid, episodedate)

Treatment1 %>% distinct(patientid) %>% nrow()
```

@@

Treatment %>% distinct(patientid) %>% nrow()
```

@@

  mutate(RDI_carbo_adj_grp = case_when(
    RDI_carbo_adj >= 0.85              ~ "Adequate dosing",
    RDI_carbo_adj < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_carbo_adj_grp = factor(RDI_carbo_adj_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_carbo_adj_grp1 = case_when(
    RDI_carbo_adj < 0.75               ~ "Highly underdosed",
    RDI_carbo_adj >= 0.75 &
      RDI_carbo_adj < 0.85             ~ "Underdosed",
    RDI_carbo_adj >= 0.85 &
      RDI_carbo_adj < 1.1              ~ "Adequate dosing",
    RDI_carbo_adj >= 1.1               ~ "Overdosing"
  )) %>% 
  mutate(RDI_carbo_adj_grp1 = factor(RDI_carbo_adj_grp1, 
                          levels = c("Adequate dosing",
                                     "Underdosed", 
                                     "Highly underdosed",
                                     "Overdosing"))) %>% 
  mutate(RDI_pacli_adj_grp = case_when(
    RDI_pacli_adj >= 0.85              ~ "Adequate dosing",
    RDI_pacli_adj < 0.85               ~ "Underdosed"
  )) %>% 
  mutate(RDI_pacli_adj_grp = factor(RDI_pacli_adj_grp, 
                           levels = c("Adequate dosing", "Underdosed"))) %>% 
  mutate(RDI_pacli_adj_grp1 = case_when(
    RDI_pacli_adj < 0.75               ~ "Highly underdosed",
    RDI_pacli_adj >= 0.75 &
      RDI_pacli_adj < 0.85             ~ "Underdosed",
    RDI_pacli_adj >= 0.85 &
      RDI_pacli_adj < 1.1              ~ "Adequate dosing",
    RDI_pacli_adj >= 1.1               ~ "Overdosing"
  )) %>% 
  mutate(RDI_pacli_adj_grp1 = factor(RDI_pacli_adj_grp1, 
                          levels = c("Adequate dosing",
                                     "Underdosed", 
                                     "Highly underdosed",
                                     "Overdosing")))
Frontline %>% distinct(patientid) %>% nrow()
```

@@

Are excluded :  
-	Borderline cases (not invasive ovarian cancer)  
-	Data from one PracticeID  (Flatiron requested removal of this practice ID from the dataset)  
-	Certain historical structured data were not available for patients seen at academic sites prior to 2015 – Flatiron has asked that if conducting survival analyses, these patients are removed (patients diagnosed < 2015 at academic sites)  
```{r}
flatiron_rec <- Frontline_adjusted %>% 
  mutate(flatiron_rules = case_when(
    days_at_first_drug > 90 | 
      days_at_surg > 90                          ~ "exclude",
    thirty_days_exclusion <= 30                  ~ "exclude",
    exclude == "1"                               ~ "exclude"
  )) %>%
  group_by(patientid) %>% 
  fill(flatiron_rules, .direction = "downup") %>% 
  ungroup()

flatiron_rec <- flatiron_rec %>% 
  filter(is.na(flatiron_rules))
```

**At the end of the step 1, we have `r flatiron_rec %>% distinct(patientid) %>% nrow()` patients.**

@@

- exclude patients whose histology is unknown  
- remove chemotherapy only patients
- include only patients who received platin and/or taxane
- exclude patients who only received neo + surgery
- include patients with single or dual P/T +/- Bev as frontline treatment
```{r}
study_criteria <- flatiron_rec %>% 
  filter(!is.na(histology)) # loss 287 ################## Will do when bind to drugs

study_criteria <- study_criteria %>%
  filter(!is.na(surgerydate))

study_criteria <- study_criteria %>%
  filter(had_carbo_pacli == "Yes")

study_criteria <- study_criteria %>% 
  filter(treatment_sequence == "neo + surg + adj" |
           treatment_sequence == "surg + adj")

@@

study_criteria <- study_criteria %>%
  # Remove patients with other linename
  filter((linenumber_new == 1 &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin")) |
          (linenumber_new == 2 &
          therapy == "Upfront Chemo" &
           (linename == "Carboplatin,Paclitaxel" |
           linename == "Bevacizumab,Carboplatin,Paclitaxel" |
           linename == "Carboplatin" |
           linename == "Bevacizumab,Paclitaxel" |
           linename == "Paclitaxel" |
           linename == "Bevacizumab,Carboplatin"))
         )
```

**At the end of the step 2, we have `r study_criteria %>% distinct(patientid) %>% nrow()` patients.**

@@

```{r}
missing_data <- study_criteria %>% 
  filter(!(issurgery == "Yes" & is.na(surgerydate)))

missing_data <- missing_data %>%
  arrange(patientid, episodedate) %>%
  mutate(ex = case_when(
    interval_surgery_to_adj_start > 3                  ~ "exclude"
  )) %>% 
  filter(is.na(ex))

missing_data <- missing_data %>% 
  filter(days_at_first_drug >= 0 &
           (is.na(surgerydate) | days_at_surg >= 0)
         )

missing_data <- missing_data %>% 
  # remove these patients who switched C > C 
  filter((!is.na(RDI_carbo_neo) & !is.na(RDI_pacli_neo) & 
            !is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj) & 
            therapy == "Upfront Chemo") |
           (!is.na(RDI_carbo_adj) & !is.na(RDI_pacli_adj &
            therapy == "Upfront Surgery")))
```
**At the end of the step 3, we have `r missing_data %>% distinct(patientid) %>% nrow()` patients.**

@@

- exclude patients with more than 1 line as Neo
- exclude patients with maintenance within their frontline
- exclude patients with more than 6 cycles in Neo, more than 9 cycles **total** in upfront chemo or more than 9 cycles in upfront surgery
```{r}
standart_care <- missing_data %>% 
  # Remove patients with more than 1 line as Neo
  filter(is.na(neo_more_more_than_1line))

standart_care <- standart_care %>% 
  filter(is.na(whole_frontline_is_maintenance))

standart_care <- standart_care %>% 
  filter(is.na(too_many_cycle))
```
**We have `r standart_care %>% distinct(patientid) %>% nrow()` patients.**

- Exclude patients that received wrong dose dense of 1 carbo + 2 paclitaxels
```{r}
Frontline <- standart_care %>% 
  filter(is.na(wrong_pacli_dosedense))

# standart_care %>% 
#   mutate(n_dose_dense = factor(n_dose_dense)) %>% 
#   select(n_dose_dense, therapy) %>% 
#   tbl_summary(by = therapy)

@@

```{r}
# missing_data %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(had_neo, had_adj, therapy) %>% 
#   tbl_summary(by = therapy,
#               type = list(had_neo ~ "dichotomous", 
#                           had_adj ~ "dichotomous"),
#               missing = "no")
# # therapy_line %>% 
# #   distinct(patientid, .keep_all = TRUE) %>% 
# #   select(therapy, treatment_sequence) %>% 
# #   tbl_summary(by = therapy)
```

<!-- First table is frontline Neo, second table is frontline Adj. -->
```{r}
# # drugs1 %>% Need to do in Frontline
#   filter(linenumber == 1
#          ) %>% 
#   distinct(patientid, .keep_all = TRUE) %>% 
#   select(linename) %>% 
#   tbl_summary(sort = list(everything() ~ "frequency"))
# 
# # missing_data %>% 
# #   filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
# #   distinct(patientid, .keep_all = TRUE) %>% 
# #   select(linename) %>% 
# #   tbl_summary(sort = list(everything() ~ "frequency"))
```

@@

As you saw, we have a big spread of RDI (it is more complicated than < or > 0.85) so I thought I could make more than 2 groups to compare patients who have a correct RDI, being underdosed or overdosed

```{r echo=TRUE}
# Highly underdosed: < 0.75
# Underdosed: >= 0.75 to <0.85
# Adequate dosing: >= 0.85 to <1.10
# Overdosing: >=1.10
```
Fun to see the dots for underdosed patients being located on the right side (higher BMI) and dots for overdosed located on the left (lower BMI)
```{r, fig.width=12, fig.height=12}
Frontline_adjusted %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(x= bmi_at_dx, y = mean_RDI_per_drug, color= RDI_grp1))+
  geom_point(alpha = 0.7, size = 0.75)+
  theme_minimal(base_size = 10)+
  facet_wrap(drugname~ therapy, ncol = 2, scales = "free")
Frontline_adjusted %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(x= bmi_cat, y = mean_RDI_per_drug, color= RDI_grp1))+
  geom_jitter()+
  theme_minimal(base_size = 10)+
  facet_wrap(drugname~ therapy, ncol = 2, scales = "free")

```
Here I just wanted to see if we have more or less underdosing / overdosing with BMI
```{r, fig.width=12, fig.height=12}
Frontline_adjusted %>% filter(!is.na(mean_RDI_per_drug)) %>%
  ggplot(aes(x= RDI_grp1, fill = drugname))+
  geom_bar(position = position_dodge())+
  theme_minimal(base_size = 10)+
  facet_wrap(. ~ therapy, ncol = 2, scales = "free")+
  coord_flip()
```

```{r, fig.width=12}
# Frontline %>% filter(!is.na(mean_RDI_per_drug)) %>%
#   ggplot(aes(x= drugname, fill = RDI_grp1))+
#   geom_bar(position = position_dodge())+
#   theme_minimal(base_size = 10)+
#   facet_wrap(drugname ~ chemotherapy_type, ncol = 2, scales = "free")+
#   coord_flip()
```

```{r}
Frontline_adjusted %>% filter(!is.na(mean_RDI_per_drug)) %>%
  # filter(linenumber_new == "1") %>%
  ggplot(aes(x= drugname, fill = RDI_grp1))+
  geom_bar(position = "fill")+
  theme_minimal(base_size = 10)+
  coord_flip()+
  facet_wrap(.~ therapy)
```
As you can see above in green, we have a lot of patient who are overdose.
<br>
<br>

## Hazard Ratio RDI 2

<span style="color:green">**Table HR**</span>

### Univariable
```{r HR RDI 2}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- tbl2 %>%
  select(vitalstatus, RDI_carbo_neo, RDI_carbo_neo_grp1) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- tbl2 %>%
  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp1) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- tbl3 %>%
  select(vitalstatus, RDI_carbo_adj, RDI_carbo_adj_grp1) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("carboplatin Neo/Upfront Chemo", 
                           "carboplatin Adj/Upfront Chemo",
                           "carboplatin Adj/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()

tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl1 <- tbl2 %>%
  select(vitalstatus, RDI_pacli_neo, RDI_pacli_neo_grp1) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl2 <- tbl2 %>%
  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp1) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl2$month_at_os_from_treatment, event = tbl2$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl3 <- tbl3 %>%
  select(vitalstatus, RDI_pacli_adj, RDI_pacli_adj_grp1) %>% 
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl3$month_at_os_from_treatment, event = tbl3$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl1, tbl2, tbl3),
          group_header = c("paclitaxel/Upfront Chemo", 
                           "paclitaxel/Upfront Chemo",
                           "paclitaxel/Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
Overdosing can help survival for carboplatin/Adjuvant Upfront Surgery and paclitaxel/Neoadjuvant ?? Loss it when choose correct as reference.
